---
title: "Homework 6"
output: html_notebook
---

| Homework 6                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Oct 11  | Business Analytics Graduate Program |
| Submit via GitHub              |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 6. Refer to the corresponding materials and
ICE (with solutions) posted on ICON. Follow all of the instructions
given on prior homeworks, referring to them as necessary.

# Exercises


# #1

Use the default read-in options to read `fires.csv` into a data frame
called `df`, and then execute the following command to save the sorted,
unique fire descriptions in a character vector called `mytext`:

    mytext <- sort(unique(as.character(df$descript)))

Then complete parts (a)-(d) below.

```{r}

```

## (a)

In a vector called `mat`, save a logical (`TRUE`/`FALSE`) vector
indicating the presence of the substring "fire" (case sensitive) in the
strings of `mytext`. Then use `mat` to save the subvector of matches
within `mytext` into a new vector called `mytext_mat`. [Hint: If done
correctly, `mytext_mat` should contain text, not logical values.]

```{r}

```

## (b)

Calculate the mean number of characters of the strings in `mytext` (not `mytext_mat`).
Save the result in `mean_chars`. [Hint: Base your calculation on *all*
characters, including spaces and punctuation. Do not round,
and do not use any kind of loop to complete this task.]

```{r}

```

## (c)

Split `mytext` by the space character and save the results in
`mylist`.

```{r}

```

## (d)

Flatten `mylist`, convert to lower case, determine the unique strings,
and sort in alphabetical order. Save the resulting sorted, lower-case
strings into a vector called `mywords`. Do not overwrite `mylist` in the
process.

```{r}

```

# #2

The included `customers.csv` contains latitude-longitude coordinates
for 7 customers---one customer per row---and the included `stores.csv`
contains latitude-longitude coordinates for 3 stores---one store per
row. The goal of this exercise is to calculate the distance (in miles)
between each customer-store pair, which is a total of 21 distances to be
calculated.

The code given below loads the data and sets up a 7-row-by-3-column
matrix, called `distances`, for storing the 21 distances. In addition,
the code calculates and properly stores the distance between the 5th
customer and the 2nd store.

Alter the code to use a nested, double for loop to calculate all 21
distances and store them in `distances`.

```{r}
# Load customers and stores data

customers <- readr::read_csv("customers.csv", show_col_types = FALSE)
stores <- readr::read_csv("stores.csv", show_col_types = FALSE)

# Create distances matrix, which will hold distances between customers
# and stores. In particular, distance[i, j] is the distance between
# customer i and store j and is stored in the i-th row and j-th column
# of the distances matrix

distances <- matrix(NA, nrow(customers), nrow(stores))

# Using temporary variables, save coordinates of 5th customer

lat_c <- customers$lat[5]
lon_c <- customers$lon[5]

# Using temporary variables, save coordinates of 2nd store

lat_s <- stores$lat[2]
lon_s <- stores$lon[2]

# Calculate the distance between the two pairs of coordinates. [Hint:
# Assume this mathematical formula is correct. You can just use it as
# is.]

lat_diff <- lat_c - lat_s
lon_diff <- lon_c - lon_s
dist <- 68.51 * sqrt(lat_diff^2 + cos(lon_s)^2 * lon_diff^2)

# Save the distance into the correct position in the distances matrix

distances[5, 2] <- dist


distances
```

# #3

The webpage https://en.wikipedia.org/wiki/Leibniz_formula_for_π
contains an interesting formula for the quantity pi/4, i.e., the number
3.141593... divided by 4. It is what you might call an "infinite"
formula because the sum includes an infinite number of terms. However,
if one stops adding after awhile, the partial/finite sum will still be
fairly close to pi/4.

If the above URL doesn't work for you (because it contains the actual
symbol for pi), you can also google "leibniz formula for pi" to locate
the Wikipedia page.

In the formula, you can notice that a term is added to/subtracted
from the sum when the denominator either leaves a remainder of 1 when
divided by 4 or leaves a remainder of 3 when divided by 4. (See the
ICE solution for code on how to calculate remainders; see also the
code below.)

The following code will compute a partial/finite sum according to
this formula, but five bits of code are missing. These bits are each
indicated by three dots (i.e., "..."). Fill in these bits of code
without altering any other parts of the code to calculate the sum.
Once completed, running the code should produce the number 0.7803987,
which is indeed not so far from pi/4 = 0.7853982.... [Note: Because of
the missing bits of code, if you try to execute the code as given, it
will produce an error.]


    pi_over_four <- ...
    for(i in 1:100) {
        if(i %% 4 == ...) {
            pi_over_four <- pi_over_four ...
        } else if(i %% 4 == ...) {
            pi_over_four <- pi_over_four ...
        }
    }


```{r}

```
